---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Design

This package is designed to apply a series of steps:
* specified by a config
* to two input fastq files resulting from pair-end MiSeq sequencing
* producing a list of results called all results
* and a set of comprehensive reports.


Given two input fastq files resulting from pair-end MiSeq sequencing and a
number of options, MotifBinner2 will apply a series of operations to the input
data. The operations are highly structured. Each operation has an action
function that performs the operation on the data given to it. This function
packages the result and a large set of metrics describing the operation into a
list and assigns a class to the list using R's S3 system. S3 is an extremely
basic class system that allows methods to be overloaded for specific datatypes.
In addition to the its action function which serves as a constructor, each
operation also has a computeMetrics, saveToDisk and print method. Lastly, for
each operation, an Rmarkdown template must be provided. Then the genReport
function is calles on a result list, then it will extract the class of the
result and use it to match the result list to a suitable template. The
genReport function will then call knitr::knit to generate an html report for
the result list.

The series of operations that must be performed is controlled by a config list.



## The vignette template

Keep it for easy reference for now.

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
