```{r include=FALSE}
opts_chunk$set(echo=FALSE)
opts_chunk$set(warning=FALSE)
opts_chunk$set(fig.pos = 'H')

library(MotifBinner2)

if (!exists('result'))
{
  result <- all_results[[grep('removeChars', names(all_results))[1]]]
}
if (class(result) != 'removeChars')
{
  result <- all_results[[grep('removeChars', names(all_results))[1]]]
}
```
# `r result$config$op_full_name`

Removes characters from the sequences.

Characters to remove: `r result$config$op_args$char_to_remove`

`r sum(result$metrics$per_read_metrics$n_gaps > 0)` of the sequences contained this character.

On average `r mean(result$metrics$per_read_metrics$n_gaps[result$metrics$per_read_metrics$n_gaps > 0])` of the character were removed from a sequence if the sequenced contained at least one of the character.

In total `r sum(result$metrics$per_read_metrics$n_gaps[result$metrics$per_read_metrics$n_gaps > 0])` of the character were removed.

```{r, results='asis'}
kable_summary(result$summary)

timingTable(result)
```

```{r, results='asis'}
cat('\n\n---\n\n')
```
